%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional experiences}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Platform Engineer} % Job title
    {Mollie} % Organization
    {Milan, Italy} % Location
    {2024, Nov. - present} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Responsibilities: Develop, maintain, and support features based on financial services integrated with Machine Learning models.}
            \item {Technologies: Back-end (Java/Spring Boot), Docker, Datadog, Redis, MySQL, Terraform, K8s environment, and Google Cloud Services.}
            \item {Projects: Design a credit automation system to enable loans for customers integrating many thrid-parties libraries like DocuSign and CoFace, and many internal services in a event-driven architecture.}
          \end{cvitems}
    }
\\
%---------------------------------------------------------
  \cventry
    {Senior Platform Engineer} % Job title
    {MotorK} % Organization
    {Milan, Italy} % Location
    {2023, Mar. - 2024, Aug.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Responsibilities: Develop, maintain, and support features based on integration needs between all the products. All support and create pipelines for CI/CD and administration of support systems like Keycloak.}
            \item {Technologies: Back-end (Java), Front-end (VueJS/TypeScript), Docker, Grafana, Loki, Keycloak, Apache Kafka, Redis, PostgreSQL, MySQL, Jenkins, Terraform, K8s environment, and AWS Cloud Services.}
            \item {Projects: Lead an authentication project for a SSO tool based on Keycloak for orchestrate external and internal authentication in the systems. This project required a cross-team orchestraction involving 10 different products. Design a backstage system to orchestrate the creation of different product instances for each client. Also, it keeps updating, using messaging exchange, all the products database.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Viator, TripAdvisor} % Organization
    {Lisbon, Portugal} % Location
    {2021, Dec. - 2023, Jan.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Responsibilities: Develop and maintain features based on inspiration content to help the user choose the product based on travel's destination, support QA automation tests like unit, integration, and snapshot tests. Monitoring and supporting the production environment, following up AB tests for new or modified features, maintenance and optimizing the CI/CD and build process.}
            \item {Technologies: Back-end (Java, TypeScript, PHP), Front-end (React/TypeScript, Dust), Docker, ElasticSearch Stack (ELK stack), Apache Solr, Redis, PostgreSQL, MySQL, Jenkins, Gitlab CI/CD, K8s environment, and AWS Cloud Services.}
            \item {Projects: During this time in Viator, I delivered two big projects from scratch. The first one is Viator's blog homepage (https://www.viator.com/blog). The other project delivered recently was the itinerary page for destinations. This project interacts with Google Maps and several page elements; find an example here: https://www.viator.com/blog/San-Francisco/d651/3-Days-in-San-Francisco-for-Foodies/i96381. Beyond that, I'm also one of the developers responsible for creating React components as part of Viator's Design System, working along with the designer's team.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Aubay Portugal} % Organization
    {Lisbon, Portugal} % Location
    {2021, Dec. - 2023, Feb.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Full stack software engineer in Viator, a sub-brand of TripAdvisor.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Software Engineer} % Job title
    {Freelancer} % Organization
    {Remote} % Location
    {2018, Jan. - current} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Projects:}
            \begin{cvsubentries}
              \cvsubentry{}{- Cognitive Chatbot using IBM Watson, Text to Speech, Speech to Text, and Image Recognition for a movie theater company. The bot can find the nearest theater and next movie, make orders, and FAQ. The chatbot integrates with a front-end component for the company's website, Facebook Messenger, Telegram, and WhatsApp. The back-end service used Spring Boot/Java to integrate with the Google Cloud Platform and IBM Cloud. Front-end chat component was with React/TypeScript}{2021, Jan. - 2021, Jun.}{}
              \cvsubentry{}{- HR Onboarding System with React for front-end, back-end in Spring Boot/Java and Oracle as database}{2020, Aug. - 2020, Nov.}{}
              \cvsubentry{}{- Create a microservices architecture to split the monolithic system of an energy company. All the microservices were created using a DDD concept and developed with Spring Boot/Java. Most databases used were relational, like MySQL and PostgreSQL; however, some services where data are not structured use MongoDB. The microservices were deployed into a K8s environment in a private cloud.}{2019, Jul. - 2020, May.}{}
              \cvsubentry{}{- Dashboard to monitor financial indicators for a private bank. The data are consumed from a datalake and converted into a Hadoop environment using Scala and Java.}{2018, Dec. - 2019, Apr.}{}
              \cvsubentry{}{- Customized architecture and coding training and workshops.}{2018, Jan. - current}{}
            \end{cvsubentries}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Professor} % Job title
    {FIAP} % Organization
    {Sao Paulo, Sao Paulo, Brazil} % Location
    {2018, Apr. - 2021, Oct.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Lectures about Responsive Web Development using Java, JSP, JSF, JavaScript, HTML5, CSS3, Bootstrap, Servlet, React, JQuery, and JQueryUI. Artificial Intelligence and Chatbots with Python. Microservices and SOA architecture with Spring Boot. Hybrid Mobile Development with React Native.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Coordinator and Professor} % Job title
    {Metodista Univesity of Sao Paulo} % Organization
    {Sao Bernardo do Campo, Sao Paulo, Brazil} % Location
    {2013, Aug. - 2020, Fev.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Lead of Programming Computer program with the main languages as Java and Python.}
            \item {Traditional and Online Learning Professor. Lectures about Oriented Object Programming, Algorithms and Data Structure, Web Application Development, Distributed Systems, Graphic Computing (OpenGL/ WebGL), Design Patterns, Robotics and Artificial Intelligence, and Computational Intelligence. Thesis Supervisor for undergraduate students and specialist students.}
            \item {Coordinated the study group for programming competitions and digital games.}
            \item {Online Course Coordinator in System Analysis and Develop Tech.}
            \item {Mentor on Information System, Computing Engineering, and Project Management courses.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {CPM Braxis Capgemini} % Organization
    {Sao Paulo, Sao Paulo, Brasil} % Location
    {Abr. 2010 - Mar. 2011} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Responsibilities: Requirement Analysis, Application of RUP methodology on software documentation, Application of Scrum for a project manager, UML diagrams, Team activities planning, Team schedule managing, Function point measuring.}
            \item {Technologies: Developed web application using C\#.Net and ASP.NET MVC.}
            \item {Applying eXtreming Programming techniques, the team delivered the control taxes system project three months earlier than expected.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {VOLANS} % Organization
    {Sao Paulo, Sao Paulo, Brazil} % Location
    {2008, May. - 2010, Apr.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Responsibilities: Outsourcing contractor inside Santander, responsible for managing meetings with stakeholders to analyze and develop ATM features like withdrawal, loan, and printing. Team Member of integration project between Santander and Real (ABN Amro) Banks.}
            \item {Technologies: Embedded systems using Java and C++, Windows DLL developed with COBOL and Visual Basic 6, front-end with JavaScript.}
            \item {Projects: Create a function to improve the withdrawal feature on the ATM. It lets the use in 35\% faster on the withdrawal option.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Rodobens Locação de Veículos} % Organization
    {Sao Bernardo do Campo, Sao Paulo, Brazil} % Location
    {2008, Jan. - 2008, May.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Optimization of process using BPMN.}
            \item {Member of Strategic Planning Committee.}
            \item {Develop and maintenance of system modules according to user requirements.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {A\&M Sistemas} % Organization
    {Sao Paulo, Sao Paulo, Brazil} % Location
    {2007, Mar. - 2008, Jan.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Develop systems using Linux (Server/Dev), Cobol/VSAM, JavaScript, HTML/DHTML.}
            \item {Create a module to control truck tire consumption using AJAX client and COBOL server sides.}
            \item {Project Client: Rodobens Locação de Veículos.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern - System Audit} % Job title
    {GOL Airlines} % Organization
    {Sao Paulo, Sao Paulo, Brazil} % Location
    {2006, Jun. - 2007, Mar.} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Internal Control with Sarbanes-Oxley (SOX).}
            \item {IT Control with COBIT.}
          \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Engineer} % Job title
    {EGO Informática} % Organization
    {Sao Bernardo do Campo, Sao Paulo, Brazil} % Location
    {Nov. 2003 - Mai. 2006} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Develop a news database for the website using Java.}
            \item {Computer maintenance.}
            \item {Telephone central maintenance.}
            \item {User Support by e-mail, telephone, or personally.}
          \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
